A Mechanised Library for Generic (Co)Programming

### 2024-01-23 paper/paper.tex
cata, ana, hylo, mutu and accumulators.

\newcommand{\anamor}[1]{{\llens\, #1\, \rlens}}
\newcommand{\catamor}[1]{\lbans\, #1\, \rbans}
\newcommand{\cata}[1]{\lbans #1 \rbans}
\newcommand{\ana}[1]{\llens #1 \rlens}
\newcommand{\fold}[1]{\catamor{#1}}
\newcommand{\unfold}[1]{\anamor{#1}}
\newcommand{\comp}{\cdot}
\newcommand{\operator}[1]{\textsf{#1}}
\newcommand{\Alg}{\text{-Alg}}
\newcommand{\Free}{\text{Free\xspace}}

\newcommand{\CatC}{\mathcal{C}}
\newcommand{\CatD}{\mathcal{D}}
\newcommand{\CatE}{\mathcal{E}}
\newcommand{\CatI}{\mathcal{I}}

@@

>>>>

\newcommand{\anamor}[1]{{\llens\, #1\, \rlens}}
\newcommand{\catamor}[1]{\lbans\, #1\, \rbans}
\newcommand{\cata}[1]{\lbans #1 \rbans}
\newcommand{\ana}[1]{\llens #1 \rlens}
\newcommand{\hylo}[2]{\text{hylo}\;#1\;#2}
\newcommand{\fold}[1]{\catamor{#1}}
\newcommand{\unfold}[1]{\anamor{#1}}
\newcommand{\comp}{\cdot}
\newcommand{\operator}[1]{\textsf{#1}}
\newcommand{\Alg}{\text{-Alg}}
\newcommand{\Free}{\text{Free\xspace}}
\newcommand{\fmap}[1]{\text{fmap}\;#1}
\newcommand{\Inop}{\operator{In}^{\circ}}
\newcommand{\In}{\operator{In}}
\newcommand{\CatC}{\mathcal{C}}
\newcommand{\CatD}{\mathcal{D}}
\newcommand{\CatE}{\mathcal{E}}
\newcommand{\CatI}{\mathcal{I}}

@@

\section{Recursive Equations}
\subsection{Catamorphisms and Anamorphism}
A catamorphism is the unique program defined as
\[
  x = a \comp \fmap{x} \comp \Inop
\]
Can be implemented:
\[
  \cata{a} = \hylo{a}{\Inop}
\]

An anamorphism is the unique program satisfying the equation
\[
  x = \In \comp \fmap{x} \comp{c}
\]
and can be implemented by hylomorphisms
\[
  \ana{c} = \hylo{\In}{c}
\]

\subsection{Accumulators}
For an algebra $a : D(A^{P}) \to A$:
\begin{align*}
  & x : (\mu F, A) \to B\\
  & x (d, p) = a (\fmap{(\curry f)} \comp \Inop(d), p)
\end{align*}

\subsection{Mutu-Hylo}
For an algebra $a_{1} : D(A_{1} \times A_{2}) \to A_{1}$ and an algebra
$a_{2} : D(A_{1} \times A_{2}) \to A_{2}$:
\begin{align*}
  & (f,g) : (\mu F, \mu F) \to (B_{1}, B_{2})\\
  & (f,g) = (a_{1}, a_{2}) \comp (\fmap{\pair{f}{g}},\fmap{\pair{f}{g}}) \comp (\Inop, \Inop)
\end{align*}
